The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
fig 2 cap

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts (Figure 2).

@@

<!-- TODO: work this cap -->
(ref:ml) Visualization of multilayer network for social ungulate case study. Six layers are presented with individuals shown as nodes, fixed in space across layers. Layer represent combinations of two seasons (winter and summer) and three landcover class (open, forest and forage). Edges connect individuals that associated according to spatial and temporal thresholds described above.

>>>>

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
seasons and within habitat classes (Figure 2).
<!-- eg this is connecting contexts used to calculate layer similarity -->

@@

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (winter and summer) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (eg. individual "A" in summer, forest and individual "A" in winter, forest).
